### 2022-12-06 Draft_GFC.tex
avant modif

@@

They try to detect anisothropy using a method based on second order bi variate \textit{circular statistics} this allows them also to quantify the direction in which it appears. They also present an application of the method to  the flow of seawater through the Strait of Gibraltar. Tools : a parametric procedure based on the calculation of standard and confidence ellipses, well how do they do that ? and what is that. Well, It's pretty weird, they start by considering a sub image $Z_{l,l}$ of the image $Z$ and $Z(s)$ the random variable (yep nothing more on this mystery variable ), from $Z_{l,l}$ they draw $N=\{z_{1}, \ldots, z_{m}\}$ a random sample of $m$ elements, nothing is being said about this random sample. $\overrightarrow{z_{i}z_{j}}$ represents a variation of $Z(s)$ with intensity $|z_{j} - z_{i}|$ in the direction $\gamma$, being 

@@

\end{equation*}We debi

@@

\section{Mathematical framework}\label{section1}
\subsection{Construction of the binary image}\label{construction}
\paragraph{Square tiling}
Let $m$ be an integer with $m \geq 2$. Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares. We denote by $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2} $ the set of point in $S$ with interger coordinates and for $x \in \mathbb{G}_{m}$, we define $C_{m}(x)$ as
\begin{equation*}
C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S.
\end{equation*}
The $C_{m}(x)$ will be referred to as \textit{cells}, to ease up the notations we denote by $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ and $e_1$, $e_{2}$ the element of the canonical base of $\mathbb{R}^{2}$.
We denote by $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S} = (0,m)^{2}$, and $\mathbb{E}_{m} = \mathbb{E}^{(1)}_{m} \cup \mathbb{E}^{(2)}_{m}$ each $w \in \mathbb{E}_{m}$ is a segment of length $1$.
Figure \ref{fig1} shows an example of a square tiling with $m = 4$.
\begin{figure}[h]
\begin{center}
\begin{tikzpicture}[scale = 0.5]
  \draw[step = 1cm, black, thick](0,0) grid (4,4);
\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (1,1);
\draw[pattern=north west lines, pattern color=blue] (3,1) rectangle (2,2);
\foreach \x in {0,1,2,3}{
  \foreach \y in {0,1,2,3}{
  \draw[fill = red] (\x,\y) circle (2pt);
  } 
}
\end{tikzpicture}
\end{center}
\vspace{-0.25cm}
\caption{Tiling with squares for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (blue stripes) and red point of $\mathbb{G}_{m}$.}
\label{fig1}
\end{figure}

\paragraph{Discrete setting}
Using the previous square tiling, we write $S =  \underset{x \in \mathbb{G}_{m}}{\cup}  C_{m}(x)$. We assume to observe $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{G}_{m}}$, which we assume coincides with values of a stationary random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$. The stationarity hypothesis means that for all $h \in \mathbb{Z}^{2}$, 
$$\left(X_{x+h}; x \in \mathbb{Z}^{2} \right)\overset{fdd}{=} \left(X_{\scriptscriptstyle x}; x \in \mathbb{Z}^{2} \right),$$ where $fdd$ denotes finite-dimensional distributions. \\
We denote by $\rho(x) :=\text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right), \; x \in \mathbb{Z}^{2}$, the covariance function of $X$.
\vspace{-1.5cm}
\begin{figure}[H]
    {\includegraphics[scale=0.25]{GaussianUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZZZUn.pdf}}
    \vspace{-2cm}
 \caption{Generations of Gaussian random field with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with $m = 1024$, and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}
\label{fig22}
\end{figure}
Let us consider a threshold parameter $t \in \mathbb{R}$. We introduce the associated binary image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$, each cell $C_{m}(x)$ is associated to black or white according to whether $Z^{\scriptscriptstyle (m)}_{t} (x) = 0$ or $Z^{\scriptscriptstyle (m)}_{t}(x)~= 1$. 
\subsection{Perimeter of a binary image}\label{methods}
For $t \in \mathbb{R}$,let $Z^{\scriptscriptstyle (m)} = Z^{\scriptscriptstyle (m)}_{t}$ be the  binary image  $Z^{\scriptscriptstyle (m)}$ at that given threshold $t \in \mathbb{R}$. Following  the approach  presented in \cite{HermineAgnes},  for each edge $w \in \mathbb{E}_{m}$, we aim to know if  $w$ contributes  to the perimeter of the black component of $Z$. Making use of the additive nature of the perimeter, one can start by computing the oriented perimeter given each direction, horizontal and vertical. Let us consider the edge $w_{i}(x) := \left(x, x+e_{i}\right)$ with $i \in \{1,2\}$, $w_{i}(x)$ belongs to $C_{m}(x) \cap C_{m}(x-e_{j})$ with $i,j \in \{1,2\}$ and $i \neq j$ as soon as $w_{i}(x) \subset  \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}$.
\begin{figure}[H]
\begin{center}
\begin{tikzpicture}
    [
        box/.style={rectangle,draw=black,thick, minimum size=1cm},
    ]

@@

We assume that $\left(X_x \right)_{x \in \mathbb{G}_{m}}$ is a stationary Gaussian centered with unit variance random field let us denote \linebreak by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in~[-1, 1]$. The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $$\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = m(m-1)\sum_{1}^{2}\mathbb{E}\left(f^{(i)}(t) \right)$$  and

@@

\item if $\rho(e_i) = -1, \; \mathbb{E}\left(f^{(i)}(t) \right)= 2\left(1 - \Phi\left(\max\left(0,t\right)\right)\right).$

@@

Let us assume that $\rho(e_{i}) \in ]-1,1]$. Considering the formula for $\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t)$ and applying the stationarity hypothesis, since
\left\{ x \in \mathbb{G}_{m}; w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle  (i)}_{m}\right\} & = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_i)\subset (0,m)^{2} \right\} \\ 
& = \left\{ 0, m-1 \right\} \times \left\{ 1, m - 1\right\},
one can write that, 

@@

 with $\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right)$. \\
 We start by applying to the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ the following transformation \begin{equation*} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} - X_{\scriptscriptstyle 0}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} + X_{\scriptscriptstyle 0}\end{equation*}
Let us introduce the following Lemma, 

@@

$$\min(a,b) \leq t \leq \max(a,b) \iff\left|t - \frac{a+b}{2}\right| \leq \left| \frac{ b-a }{2}\right| $$

@@

\node[text width= 1.6cm, font=\large] at (4,1) {$\frac{|b-a|}{2}$};

@@

Thus, applying the Lemma we get 

@@

\end{align*}}Besides, the covariance matrix of the new Gaussian vector $\left(\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right)$ is given by ${\tilde{\Sigma}_{i}(0)~= M\Sigma_{i}(0) M^{\star}}$ with {\small $M = \begin{pmatrix}
Thus, $\tilde{\Sigma}_{i}(0) = \begin{pmatrix}  2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i)  \end{pmatrix}$, which directly  implies that the two variables~$\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ and $S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ are independent, we get the following system 
  \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} & = & \sqrt{2(1-\rho(e_i))}U, \textcolor{white}{(1-\rho(e_i))U + }\\
  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} & = & \textcolor{white}{(1-\rho(e_i))U + } \sqrt{2(1+\rho(e_i)}V, 
\right.$

@@

with $U, V \sim \mathcal{N}(0,I_{2})$, thus 

@@

In the independent case, $\rho(e_i) = 0$, we can write

@@

by applying a variable change {\small$\left\{\begin{array}{rcl}

@@

\label{decreasingrho}
Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result concerning the expected perimeter of the nodal curve ($t=0$).
 \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) < \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(0)\right) > \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(0)\right),
where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance $\tilde{\rho}$. 
One has $\mathbb{E}\left(f^{(i)}(0)\right) = \mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - \mathbb{E}\left(-\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) = 2\mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) -~1$. Since $\rho \mapsto \frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}$ is strictly decreasing, we see that $\rho \mapsto 2\mathbb{E}\left(\frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}|N|\right) - 1 $ is also strictly decreasing. 

@@

 \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) \leq \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) \geq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).

@@

Let $t \in \mathbb{R}$ and $X$, $Y$ two centered with unit variance Gaussian random fields on $\mathbb{Z}^{2}$ of covariance stucture respectively $\tilde{\rho}$ and $\bar{\rho}$. We assume that $\tilde{\rho}(e_i) \leq \bar{\rho}(e_i)$, and consider the Gaussian vectors $\left(X_{0}, X_{e_1}\right)$ and $\left(Y_{0}, Y_{e_1}\right)$, $\tilde{\rho}(e_i) \leq \bar{\rho}(e_i)$ implies that $\mathbb{E}\left(X_{0}X_{e_1}\right) < \mathbb{E}\left(Y_{0}Y_{e_1}\right)$, we can write that

@@

\mathbb{P}\left(Y_{\scriptscriptstyle 0} < t \leq  Y_{e_1}\right) = \mathbb{P}\left(Y_{\scriptscriptstyle 0} < t\right) - \mathbb{P}\left(Y_{\scriptscriptstyle 0} < t,  Y_{e_1} < t\right),

@@

according to Slepian's lemma, $\mathbb{P}\left(X_{\scriptscriptstyle 0} < t,  X_{e_1} < t\right) \leq \mathbb{P}\left(Y_{\scriptscriptstyle 0} < t,  Y_{e_1} < t\right)$, \linebreak besides,~$\mathbb{P}\left(Y_{\scriptscriptstyle 0} < t\right)=\mathbb{P}\left(X_{\scriptscriptstyle 0} < t\right)$ thus, 
\mathbb{P}\left(Y_{\scriptscriptstyle 0} < t \leq  Y_{e_1}\right) \leq \mathbb{P}\left(X_{\scriptscriptstyle 0} < t \leq  X_{e_1}\right)
and,
\mathbb{P}\left(\min\left(Y_{\scriptscriptstyle 0}, Y_{e_1}\right) < t \leq \max\left(Y_{\scriptscriptstyle 0}, Y_{e_1}\right)\right)  \leq \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_1}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_1}\right)\right) 
\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) \geq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).

@@

Considering the contraposition of this result, we get the following 
 \text{if} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) \neq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right)   \hspace{0.5cm} \text{then}  \hspace{0.5cm} \tilde{\rho}(e_i) \neq \bar{\rho}(e_i) \hspace{0.5cm}.

@@

Let $s, t \in \mathbb{R}$ such that $t \leq s$. Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$.

@@

@@

\text{Cov}(\mathcal{P}_{m}(t), \mathcal{P}_{m}(s))  & = \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) \\
& + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) .

@@

With 

@@

& = \sum_{x_1=2-m}^{m-1} \sum_{x_2 = 1-m}^{m-2} \left(m-|x_1| - \mathbbm{1}_{x_{1} \leq 0}\right)\left(m-|x_2|-\mathbbm{1}_{x_{2} \geq 0}\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)

@@

Let us start with the computation of $\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))$, $i = 1$for $t \leq s$. 

@@

\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) &  = \sum_{z_{\scriptscriptstyle 1} = \left(2-m\right)}^{m-2}\sum_{z_{\scriptscriptstyle 2}=\left(1-m\right)}^{m-1}\left(m -1 -|z_{1}|\right)\left(m - |z_{2}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(z) \right) 

@@

For the second part of \eqref{covariance}, we have still by stationarity

@@

Getting the value of the covariance requires the computation of all the \linebreak elements~$\text{Cov}\left(f_{t}^{\scriptscriptstyle (j)}(0), f_{s}^{\scriptscriptstyle (i)}(x)\right)$, $i,j \in\{1,2\}$ which has a two, three and four cell structure. 
Figure \ref{configurations} below shows the five types of configurations depending on the orientation $i$ and position on the grid $x$. 

@@

\caption{Illustration of the two three and four cells configuration involved in the study of $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right)$ in Lemma \ref{CovLemma}.}

@@

Let us first start with the two cell case, which appears in the computation of the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$, in order to compute it, we just have to apply the same strategy we used to compute the first moment in Proposition \ref{propFisrtmoment}. Thus, We get the next result. \\

@@

>>>>

 \newcolumntype{C}[1]{>{\centering\arraybackslash$}p{#1}<{$}}

@@

They try to detect anisothropy using a method based on second order bi variate \textit{circular statistics} this allows them also to quantify the direction in which it appears. They also present an application of the method to  the flow of seawater through the Strait of Gibraltar. Tools : a parametric procedure based on the calculation of standard and confidence ellipses. Well, It's pretty weird, they start by considering a sub image $Z_{l,l}$ of the image $Z$ and $Z(s)$ the random variable (yep nothing more on this mystery variable ), from $Z_{l,l}$ they draw $N=\{z_{1}, \ldots, z_{m}\}$ a random sample of $m$ elements, nothing is being said about this random sample. $\overrightarrow{z_{i}z_{j}}$ represents a variation of $Z(s)$ with intensity $|z_{j} - z_{i}|$ in the direction $\gamma$, being 

@@

@@

\section{Mathematical framework}\label{section1}
\subsection{Construction of the binary image}\label{construction}
\paragraph{Square tiling}
Let $m$ be an integer with $m \geq 2$. Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares. We denote by 
\item $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2}$ the set of points in $S$
\item $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S}$,
\item for $x\in \mathbb{G}_{m}, \; C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S.$
The $C_{m}(x)$ will be referred to as \textit{cells}. To ease up the notations we write $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ for any $x\in \mathbb{G}_{m}$ and $e_1$, $e_{2}$ the elements of the canonical base of $\mathbb{R}^{2}$.
Each $w \in \mathbb{E}^{(i)}_{m}$ is a segment of length $1$. 
\begin{remark} The cardinality of the set $\mathbb{E}^{\scriptscriptstyle  (i)}_{m}$
\label{cardEm}
\item 
$\left\{ x \in \mathbb{G}_{m}; w_{1}(x) \in \mathbb{E}^{\scriptscriptstyle  (1)}_{m}\right\} = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_1)\subset (0,m)^{2} \right\} $\\ 
 \hspace*{4.25cm}$ =  \left\{ 1, m - 1\right\}\times\left\{ 0, m-1 \right\},$
\item$\left\{ x \in \mathbb{G}_{m}; w_{2}(x) \in \mathbb{E}^{\scriptscriptstyle  (2)}_{m}\right\}  = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_2)\subset (0,m)^{2} \right\} $\\ 
 \hspace*{4.25cm}$ = \left\{ 0, m-1 \right\} \times \left\{ 1, m - 1\right\},$
Figure \ref{fig1} shows an example of a square tiling with~$m = 4$.
\begin{figure}[h]
\begin{tikzpicture}[scale = 0.5]
  \draw[step = 1cm, black, thick](0,0) grid (4,4);
\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (1,1);
\draw[pattern=north west lines, pattern color=blue] (3,1) rectangle (2,2);
\foreach \x in {0,1,2,3}{
  \foreach \y in {0,1,2,3}{
  \draw[fill = red] (\x,\y) circle (2pt);
\caption{Tiling with squares for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (blue stripes) and red point of $\mathbb{G}_{m}$.}
\paragraph{Discrete setting}
Using the previous square tiling, we write $S =  \underset{x \in \mathbb{G}_{m}}{\cup}  C_{m}(x)$. We assume to observe $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{G}_{m}}$, which we assume coincides with values of a stationary random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$. The stationarity hypothesis means that for all $h \in \mathbb{Z}^{2}$, 
$$\left(X_{x+h}; x \in \mathbb{Z}^{2} \right)\overset{fdd}{=} \left(X_{\scriptscriptstyle x}; x \in \mathbb{Z}^{2} \right),$$ where $fdd$ denotes finite-dimensional distributions. \\
We denote by $\rho(x) :=\text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right), \; x \in \mathbb{Z}^{2}$, the covariance function of $X$.
\vspace{-1.5cm}
    {\includegraphics[scale=0.25]{GaussianUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZZZUn.pdf}}
    \vspace{-2cm}
 \caption{Generations of Gaussian random fields with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with $m = 1024$, and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}
\label{fig22}
Considering a threshold parameter $t \in \mathbb{R}$, we introduce the associated binary image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$, each cell $C_{m}(x)$ is associated to black or white according to whether $Z^{\scriptscriptstyle (m)}_{t} (x) = 0$ or $Z^{\scriptscriptstyle (m)}_{t}(x)~= 1$. 
\subsection{Perimeter of a binary image}\label{methods}
For $t \in \mathbb{R}$, let $Z^{\scriptscriptstyle (m)} = Z^{\scriptscriptstyle (m)}_{t}$ be the  binary image at that given threshold $t \in \mathbb{R}$. Following  the approach  presented in \cite{HermineAgnes},  for each edge $w \in \mathbb{E}_{m}$, we aim to know if  $w$ contributes  to the perimeter of the black component of $Z$. Making use of the additive nature of the perimeter, one can start by computing the oriented perimeter given each direction, horizontal and vertical. Let us consider the edge $w_{i}(x) := \left(x, x+e_{i}\right)$ with $i \in \{1,2\}$, $w_{i}(x)$ belongs to $C_{m}(x) \cap C_{m}(x-e_{j})$ with $i,j \in \{1,2\}$ and $i \neq j$ as soon as $w_{i}(x) \subset  \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}$.
\begin{tikzpicture}
    [
        box/.style={rectangle,draw=black,thick, minimum size=1cm},
    ]

@@

We assume that $\left(X_x \right)_{x \in \mathbb{G}_{m}}$ is a stationary Gaussian centered with unit variance random field. Let us denote \linebreak by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in~[-1, 1]$. The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $$\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = m(m-1)\sum_{1}^{2}\mathbb{E}\left(f^{(i)}(t) \right)$$ where

@@

\item if $\rho(e_i) = -1, \; \mathbb{E}\left(f^{(i)}(t) \right)= 2\left(1 - \Phi\left(|t|\right)\right).$

@@

Let us assume that $\rho(e_{i}) \in ]-1,1]$. Considering the formula for $\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t)$ and applying the stationarity hypothesis and Remark \ref{cardEm} one can write that, 

@@

 with $\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right)$. Before going any further, let us first make the following remark, 

@@

$$\min(a,b) \leq t \leq \max(a,b) \iff\left|2t - (a+b))\right| \leq \left| b-a \right| $$

@@

\node[text width= 1.6cm, font=\large] at (4,1) {$|b-a|$};

@@

We start by applying to the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ the following transformation \begin{equation*} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} - X_{\scriptscriptstyle 0}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} + X_{\scriptscriptstyle 0}, \end{equation*} 
the covariance matrix of the new Gaussian vector $\left(\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right)$ is given by ${\tilde{\Sigma}_{i}(0)~= M\Sigma_{i}(0) M^{\star}}$ with {\small $M = \begin{pmatrix}
Thus, $\tilde{\Sigma}_{i}(0) = \begin{pmatrix}  2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i)  \end{pmatrix}$, which directly  implies that the two variables~$\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ and $S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ are independent. Hence, we can write
  \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} & = & \sqrt{2(1-\rho(e_i))}U, \\
  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} & = & \sqrt{2(1+\rho(e_i)}V, 
\right.$ \linebreak with~$(U, V) \sim \mathcal{N}\left(0, I_{2}\right)$. Thus, applying Remark \ref{lemmasommediff} above we get 

@@

@@

with $(U, V) \sim \mathcal{N}(0,I_{2})$, thus 

@@

In the independent case \textit{i.e.} $\text{Cov}\left(X_{0}, X_i\right) = 0$, we can write

@@

by applying the variable change {\small$\left\{\begin{array}{rcl}

@@

@@

 \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) < \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) > \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).

@@

Let $t \in \mathbb{R}$ we can prove this result by considering  the function $$h:x\mapsto \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right) - \Phi\left(\dfrac{2t - \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right).
$$
with $N \sim \mathcal{N}\left(0,1\right)$, its derivative is equal to 

@@

h'(x) &= \frac{2\exp(-t^2/(1+x))}{2\sqrt{2\pi}(1-x)^{1/2}(1+x)^{3/2}}\\
& \int_{0}^{\infty}\exp\left(-\frac{N^{2}}{(1+x)}\right)\left(-4N\cosh\left(\frac{t\sqrt{2(1-x)}}{1+x}\right) + 2t\sqrt{2(1-x)}\sinh\left( \frac{t\sqrt{2(1-x)}}{1+x}\right)\right)dN \\
& = \frac{-2\exp(-t^2/(1+x))(1+x)}{\sqrt{2\pi}(1-x)^{1/2}(1+x)^{3/2}}\\
& = \frac{-2}{\sqrt{2\pi(1-x^2)}}\exp(-t^2/(1+x)),

@@

for all $|x| < 1, \; h'(x) < 0$, thus, $h$ is a strictly decreasing function. 

@@

@@

Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$.

@@

Let $s, t \in \mathbb{R}$, 

@@

\text{Cov}(\mathcal{P}_{m}(t), \mathcal{P}_{m}(s))  & = \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) \nonumber \\
& + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)),

@@

@@

& = \sum_{x_1=2-m}^{m-1} \sum_{x_2 = 1-m}^{m-2} \left(m-|x_1| - \mathbbm{1}_{x_{1} \leq 0}\right)\left(m-|x_2|-\mathbbm{1}_{x_{2} \geq 0}\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right).

@@

Let us start with the computation of $\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))$. 

@@

\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) &  = \sum_{z_{\scriptscriptstyle 1} = \left(2-m\right)}^{m-2}\sum_{z_{\scriptscriptstyle 2}=\left(1-m\right)}^{m-1}\left(m -1 -|z_{1}|\right)\left(m - |z_{2}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(z) \right). 

@@

For the last part of \eqref{covariance}, we have still by stationarity

@@

Getting the value of the covariance $\text{Cov}\left(\mathcal{P}_{m}(t),\mathcal{P}_{m}(s)\right)$ requires the computation of all the \linebreak elements~$\text{Cov}\left(f_{t}^{\scriptscriptstyle (j)}(0), f_{s}^{\scriptscriptstyle (i)}(x)\right)$, $i,j \in\{1,2\}$ which has a two, three or four cells structure, depending on the cardinality of the set $\{C_{m}(0), C_{m}(e_1), C_{m}(x), C_{m}(x+e_i)\}$. 
Figure \ref{configurations} below shows the five types of configurations depending on the orientation $i$ and the position of $x$ on the grid. 

@@

\caption{Illustration of the two, three and four cells configuration involved in the computation of $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right)$ in Lemma \ref{CovLemma}.}

@@

Let us first start with the two cells case, which appears in the computation of the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$. Applying the same strategy we used to compute the first moment in Proposition \ref{propFisrtmoment}, we get the next result. \\

@@

Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance of covariance sturcture given by $\rho$, such that $|\rho(e_i)| < 1$
